%
% File: abstract.tex
% Author: Abhushan Sahu
% Description: Contains the text for thesis abstract
%
% UoB guidelines:
%
% Each copy must include an abstract or summary of the dissertation in not
% more than 300 words, on one side of A4, which should be single-spaced in a
% font size in the range 10 to 12. If the dissertation is in a language other
% than English, an abstract in that language and an abstract in English must
% be included.

\chapter*{Abstract}
\begin{SingleSpace}
\initial{T}he purpose of my project was to model how a certain change in posture of a human body, can be used to determine the ambiance, and thereby working accordingly. Similar tests are used by car manufacturers to signal the airbags to inflate when needed. In testing, subject was regulated to conditions that can result in harm, under laboratory conditions. \\

The research is named under the line, `A Study in Fall', Where the whole study is concentrated during the fall/jerk/accident of the user. The data gathered and assessment that works for is done inside the event. Hence the name, a study `in' fall, rather than `on' or `of'. The research/project has been escorted/guided with the help of two professional doctors. Hence the correctness of the study is in favor of us.\\

I conducted several experiments using myself, and some few volunteers. I further added the knowledge of statistics to determine a pattern in the data. For each experiment, subject has to undergo a fall, or an unexpected anomaly in motion. Further refining of data using R processing, gave a clear window. Detailed study and whole story has been revealed on the inside of the book.\\

The practical implementation aka the project is named, `Helpr'. This is a cell phone application, that works under the climactic part of any accident. Basically the provision of this application work under a very delicate situation when the life of a user hangs in balance, literally. It being a post alarming application activates its procedure after any calamity happens, though it runs always in the background as a service to the phone. With having just a tiny bit of overhead charge for the battery or processing, which is closely negligible.\\

The algorithm is subject to change/update in accordance with future experiments. I initially used the upper bound function, which after a few trials is captured in a window(stated inside). This whole experimentation and real-time data, helps in creation of the application from dust. \\

Further, the structuring and coding part is done under android environment with java as the primary language, this was chosen as it being popular at the time of its creation.


\end{SingleSpace}
\clearpage